---
output: 
    html_document:
        keep_md: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(dpi = 300,
                      fig.path="README_files/")
```

# skyscraper

This R data package -- as of November 25, 2015 -- provides the data for the 100 Tallest Completed Buildings in the World as listed by [The Skyscraper Center](http://www.skyscrapercenter.com/buildings).

This tbl_df includes 9 variables:

```{r message=FALSE, echo=FALSE}
library(dplyr)
library(tidyr)

library(skyscraper)

skyscraper %>% 
  summarise_each(funs(class)) %>% 
  gather(variable, class) %>% 
  knitr::kable(format = "markdown")
```

## Install
You can install `skyscraper` from GitHib:
```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("csiu/skyscraper")
```

### ... and test drive
```{r testdrive}
library(skyscraper)
library(ggplot2)


ggplot(skyscraper, 
       aes(
         x = reorder(city, height_m, function(x){-max(x)}), 
         y = height_m
       )) +
  geom_point() + 
  xlab("") + 
  ylab("Height (m)") +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)
  )
```

## Plain text file
I make available the plain text, comma delimited `.csv` file of the skyscraper data:

- [`skyscraper.csv`](inst/skyscraper.csv): the same dataset available via `library(skyscraper); skyscraper`
- If this package is installed on your system, you can find this file via: `system.file("skyscraper.tsv", package="skyscraper")`

## Acknowledgement
This data is from: 

> Skyscrapercenter.com,. (2015). *100 Tallest Completed Buildings in the World - The Skyscraper Center.* Retrieved 25 November 2015, from http://www.skyscrapercenter.com/buildings
